Milk intake and stroke mortality in the Japan Collaborative Cohort Study - a Bayesian survival analysis

### 2020-07-14 Paperfolder/Paperfolder.Rmd
Updated almost everything except abstract

---
title: Milk intake and stroke mortality in the Japan Collaborative Cohort Study - a Bayesian survival analysis 
author:
  - name: Chaochen Wang
    affil: 1,*
    orcid: 0000-0001-5533-1497
  - name: Hiroshi Yatsuya
    affil: 2 
    orcid: 0000-0002-6220-9251
  - name: Yingsong Lin
    affil: 1
    orcid: 0000-0003-0214-3649
  - name: Tae Sasakabe 
    affil: 1 
    orcid: 0000-0002-7417-5693
  - name: Sayo Kawai
    affil: 1
    orcid: 0000-0002-5156-4880
  - name: Shogo Kikuchi
    affil: 1
    orcid: 0000-0001-9499-9668
  - name: Hiroyasu Iso
    affil: 3
    orcid: 0000-0002-9241-7289 
  - name: Akiko Tamakoshi
    affil: 4
    orcid: 0000-0002-9761-3879 
affiliation:
  - num: 1
    address: |
      Department of Public Health, Aichi Medical University School of Medicine, Nagakute, Japan
#    email: chaochen@wangcc.me
  - num: 2
    address: |
      Departmet of Public Health, Fujita Health University School of Medicine, Toyoake, Japan
  - num: 3
    address: |
      Public Health, Department of Social Medicine, Osaka University Graduate School of Medicine, Osaka, Japan
  - num: 4
    address: |
      Department of Public Health, Faculty of Medicine, Hokkaido University, Sapporo, Japan
#    email: yatsuya@gmail.com
# firstnote to eighthnote
# firstnote: |
#   Current address: Updated affiliation
# secondnote: |
#   These authors contributed equally to this work.
correspondence: |
  Email.: chaochen@wangcc.me; Tel.: +81-561-62-3311. Department of Public Health, Aichi Medical University School of Medicine, 1-1 Yazakokarimata, Nagakute, Aichi, 480-1195, Japan (C.W.)
journal: nutrients
type: article
status: submit
bibliography: milk.bib
# appendix: appendix.tex
# simplesummary: |
#  A Simple summary goes here.
abstract: |
  A single paragraph of about 200 words maximum. For research articles, 
  abstracts should give a pertinent overview of the work. We strongly encourage
  authors to use the following style of structured abstracts, but without 
  headings: 1) Background: Place the question addressed in a broad context and
  highlight the purpose of the study; 2) Methods: Describe briefly the main
  methods or treatments applied; 3) Results: Summarize the article's main 
  findings; and 4) Conclusion: Indicate the main conclusions or interpretations. 
  The abstract should be an objective representation of the article, it must not 
  contain results which are not presented and substantiated in the main text and 
  should not exaggerate the main conclusions.
keywords: |
  milk intake; mortality; stroke; Bayesian survival anlysis; time-to-event data; JACC study 
acknowledgement: |
  All sources of funding of the study should be disclosed. Please clearly 
  indicate grants that you have received in support of your research work. 
  Clearly state if you received funds for covering the costs to publish in open 
  access.
authorcontributions: |
  ``X.X. and Y.Y. conceive and designed the experiments; X.X. performed the 
  experiments; X.X. and Y.Y. analyzed the data; W.W. contributed 
  reagents/materials/analysis tools; Y.Y. wrote the paper.''
conflictsofinterest: |
  The authors declare no conflict of interest. The founding sponsors had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, an in the decision to publish the results.
# sampleavailability: |
#   Samples of the compounds ...... are available from the authors.
abbreviations:
  - short: JACC
    long: Japan Collaborative Cohort 
  - short: FFQ
    long: Food Frequency Questionnaire
  - short: MCMC
    long: Markov Chain Monte Carlo
  - short: JAGS
    long: Just Another Gibbs Samplers
  - short: AFT
    long: accelerated failure time 
  - short: HR
    long: hazard ratio
  - short: AF
    long: acceleration factor
  - short: sd
    long: standard deviation
  - short: CrI
    long: credible interval
header-includes:
   - \usepackage{graphicx}
output: rticles::mdpi_article
---

@@

<!-- - comparison with previous meta-analysis -->
These findings are in line with our previous report [@wang_milk_2015]. Moreover, we further updated with more comprehensive and more straightforward evidence about whether and how certain the evidence had shown about daily consumption of milk is contributing to a postponed stroke (mostly cerebral infarction) mortality event among Japanese men. A recent dose-response meta-analysis of 18 prospective cohort studies had also shown a similar negative association [@DeGoede2016] between milk consumption and risk of stroke. The same meta-analysis however also found a slightly higher risk of stroke per 200 g/day whole milk intake from five cohort studies that were conducted on European or American population [@goldbohm2011dairy; @Iso1999]. 
<!-- - potential biological reasons -->

<!-- - strength and limitation of current study -->

# Conclusion

@@

\rowcolor{gray!6}  \hspace{1em}MeanHR (SD) & 1 & 0.98 (0.11) & 0.84 (0.08) & 0.86 (0.08) & 0.76 (0.05)\\

@@

\hspace{1em}MeanHR (SD) & 1 & 1.01 (0.12) & 0.87 (0.09) & 0.90 (0.09) & 0.80 (0.07)\\

@@

\hspace{1em}MeanHR (SD) & 1 & 1.03 (0.19) & 0.82 (0.14) & 0.84 (0.15) & 0.97 (0.13)\\

@@

\rowcolor{gray!6}  \hspace{1em}MeanHR (SD) & 1 & 1.11 (0.21) & 0.88 (0.16) & 0.90 (0.16) & 0.88 (0.12)\\

@@

\hspace{1em}MeanHR (SD) & 1 & 1.14 (0.22) & 0.92 (0.17) & 0.95 (0.18) & 0.95 (0.14)\\

@@

\hspace{1em}MeanHR (SD) & 1 & 0.65 (0.12) & 0.59 (0.09) & 0.64 (0.09) & 0.71 (0.09)\\

@@

\rowcolor{gray!6}  \hspace{1em}MeanHR (SD) & 1 & 0.73 (0.13) & 0.65 (0.10) & 0.70 (0.11) & 0.58 (0.07)\\

@@

\hspace{1em}MeanHR (SD) & 1 & 0.73 (0.14) & 0.67 (0.11) & 0.72 (0.12) & 0.61 (0.08)\\

>>>>

---
title: Milk intake and stroke mortality in the Japan Collaborative Cohort Study - a Bayesian survival analysis 
author:
  - name: Chaochen Wang
    affil: 1,*
    orcid: 0000-0001-5533-1497
  - name: Hiroshi Yatsuya
    affil: 2 
    orcid: 0000-0002-6220-9251
  - name: Yingsong Lin
    affil: 1
    orcid: 0000-0003-0214-3649
  - name: Tae Sasakabe 
    affil: 1 
    orcid: 0000-0002-7417-5693
  - name: Sayo Kawai
    affil: 1
    orcid: 0000-0002-5156-4880
  - name: Shogo Kikuchi
    affil: 1
    orcid: 0000-0001-9499-9668
  - name: Hiroyasu Iso
    affil: 3
    orcid: 0000-0002-9241-7289 
  - name: Akiko Tamakoshi
    affil: 4
    orcid: 0000-0002-9761-3879 
affiliation:
  - num: 1
    address: |
      Department of Public Health, Aichi Medical University School of Medicine, Nagakute, Japan
#    email: chaochen@wangcc.me
  - num: 2
    address: |
      Departmet of Public Health, Fujita Health University School of Medicine, Toyoake, Japan
  - num: 3
    address: |
      Public Health, Department of Social Medicine, Osaka University Graduate School of Medicine, Osaka, Japan
  - num: 4
    address: |
      Department of Public Health, Faculty of Medicine, Hokkaido University, Sapporo, Japan
#    email: yatsuya@gmail.com
# firstnote to eighthnote
# firstnote: |
#   Current address: Updated affiliation
# secondnote: |
#   These authors contributed equally to this work.
correspondence: |
  Email.: chaochen@wangcc.me; Tel.: +81-561-62-3311. Department of Public Health, Aichi Medical University School of Medicine, 1-1 Yazakokarimata, Nagakute, Aichi, 480-1195, Japan (C.W.)
journal: nutrients
type: article
status: To be submitted
bibliography: milk.bib
# appendix: appendix.tex
# simplesummary: |
#  A Simple summary goes here.
abstract: |
  To further examine the relationship between milk intake and stroke mortality among the Japanese population. We used 
keywords: |
  milk intake; mortality; stroke; Bayesian survival anlysis; time-to-event data; JACC study 
acknowledgement: |
  The authors would like to express their sincere appreciate to Kunio Aoki and Yoshiyuki Ohno, Professors Emeritus at Nagoya University School of Medicine and former chairpersons of the JACC Study. The whole member of JACC Study Group can be found at https://publichealth.med.hokudai.ac.jp/jacc/index.html. The JACC Study has been supported by Grants-in-Aid for Scientific Research from the Ministry of Education, Culture, Sports, Science and Technology of Japan (MEXT, Monbu Kagaku-sho), Tokyo (grant numbers 61010076, 62010074, 63010074, 1010068, 2151065, 3151064, 4151063, 5151069, 6279102, 11181101, 17015022, 18014011, 20014026, 20390156, 26293138, and 16H06277), and Grants-in-Aid from the Ministry of Health, Labour and Welfare, Health and Labour Sciences Research Grants, Japan [H20-Junkankitou (Seishuu)-Ippan-013, H23-Junkankitou (Seishuu)- Ippan-005, H26-Junkankitou (Seisaku)-Ippan-001, and H29-Junkankitou (Seishuu)-Ippan-003]. 
authorcontributions: |
  ``C.W. and H.Y. conceive and designed the study; C.W. analyzed the data; C.W. wrote the first draft of the paper. A.T. provided the database. All of the authors approved and finalized the manuscript for publication.''
conflictsofinterest: |
  The authors declare no conflict of interest. The founding sponsors had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, an in the decision to publish the results.
# sampleavailability: |
#   Samples of the compounds ...... are available from the authors.
abbreviations:
  - short: JACC
    long: Japan Collaborative Cohort 
  - short: FFQ
    long: Food Frequency Questionnaire
  - short: MCMC
    long: Markov Chain Monte Carlo
  - short: JAGS
    long: Just Another Gibbs Samplers
  - short: AFT
    long: accelerated failure time 
  - short: HR
    long: hazard ratio
  - short: AF
    long: acceleration factor
  - short: sd
    long: standard deviation
  - short: CrI
    long: credible interval
header-includes:
   - \usepackage{graphicx}
output: rticles::mdpi_article
---

@@

<!-- - comparison with previous meta-analyses -->
These findings are in line with our previous report [@wang_milk_2015] as well as other studies conducted in East Asian populations [@umesawa2008dietary;@kondo2013consumption;@ozawa2017dietary;@sauvaget2003intake;@Talaei_2016]. Moreover, we have further updated with more comprehensive and straightforward evidence about whether and how certain the data had shown about daily consumption of milk is contributing to a postponed stroke (mostly cerebral infarction) mortality event among Japanese men. A recent dose-response meta-analysis of 18 prospective cohort studies had also shown a similar negative association [@DeGoede2016] between milk consumption and risk of stroke. The same meta-analysis also reported a greater reduction of risk of stroke (18%) for East Asian population in contrast with the 7% less risk in the pooled overall finding for all populations combined. Benefits of increased milk intake might be particularly noticeable in East Asian countries where strokes are relatively more common, and milk consumption is much lower than those studies conducted among European or American populations [@dehghan2018association]. 
<!-- - potential biological reasons -->

Possible reasons for a protective effect of milk consumption against stroke could be interpreted as such an association may be mediated by its content in calcium, magnesium, potassium, and other bioactive compounds, as recommended by @Iacoviello2018. Apart from the inorganic minerals in milk that would be helpful with health effects, recent studies on animal models also indicated key evidence that stroke-associated morbidity was delayed in stroke-prone rats who were fed with milk-protein enriched diets [@Chiba2012;@singh2016diets]. More precisely, @Singh2020 found that whey protein and its components lactalbumin and lactoferrin improved energy balance and glycemic control against the onset of neurological deficits associated with stroke. Bioactive peptides from milk proteins were also responsible for limitation of thrombosis [@tokajuk2019whey] through their angiotensin convertase enzyme inhibitory potential, which might partly explain why the effect was found mainly for mortality from cerebral infarction in the current study.

<!-- - strength and limitation of current study -->
Some limitations here are worth mentioning. First, although our object was not to answer which type of milk is protective, but if such information were somehow available in the JACC study database, more detailed comparison or stratification would have been possible. Second, despite reasonable validity of FFQ in the JACC study cohort was assessed and confirmed, measurement errors are inevitable. Therefore, we did not try to compute the amount of consumption by multiplying an average volume per occasion with the frequency of intake since the random error might be exaggerated and the observed associations may have attenuated. Strengths of our analyses included that we have transformed the research questions to more transparent ones that is easier for interpretation. Direct probabilities that daily milk intake is associated with lower hazard or delayed stroke mortality event were provided here after thorough computer simulation.

In conclusion, the JACC study database has provided evidence that Japanese men who consumed milk daily had lower hazard of dying from stroke especially cerebral infarction compared with their counterparts who never consumed milk. Time before an event of stroke mortality occurred were slowed down and delayed among those who drank milk regularly.

@@

\rowcolor{gray!6}  \hspace{1em}Mean HR (SD) & 1 & 0.98 (0.11) & 0.84 (0.08) & 0.86 (0.08) & 0.76 (0.05)\\

@@

\hspace{1em}Mean HR (SD) & 1 & 1.01 (0.12) & 0.87 (0.09) & 0.90 (0.09) & 0.80 (0.07)\\

@@

\hspace{1em}Mean HR (SD) & 1 & 1.03 (0.19) & 0.82 (0.14) & 0.84 (0.15) & 0.97 (0.13)\\

@@

\rowcolor{gray!6}  \hspace{1em}Mean HR (SD) & 1 & 1.11 (0.21) & 0.88 (0.16) & 0.90 (0.16) & 0.88 (0.12)\\

@@

\hspace{1em}Mean HR (SD) & 1 & 1.14 (0.22) & 0.92 (0.17) & 0.95 (0.18) & 0.95 (0.14)\\

@@

\hspace{1em}Mean HR (SD) & 1 & 0.65 (0.12) & 0.59 (0.09) & 0.64 (0.09) & 0.71 (0.09)\\

@@

\rowcolor{gray!6}  \hspace{1em}Mean HR (SD) & 1 & 0.73 (0.13) & 0.65 (0.10) & 0.70 (0.11) & 0.58 (0.07)\\

@@

\hspace{1em}Mean HR (SD) & 1 & 0.73 (0.14) & 0.67 (0.11) & 0.72 (0.12) & 0.61 (0.08)\\

### 2020-07-14 Paperfolder/Paperfolder.tex
Updated almost everything except abstract

%=================================================================
\documentclass[nutrients,article,submit,moreauthors,pdftex]{mdpi}

@@

% Abstract (Do not insert blank lines, i.e. \\)
\abstract{A single paragraph of about 200 words maximum. For research
articles, abstracts should give a pertinent overview of the work. We
strongly encourage authors to use the following style of structured
abstracts, but without headings: 1) Background: Place the question
addressed in a broad context and highlight the purpose of the study; 2)
Methods: Describe briefly the main methods or treatments applied; 3)
Results: Summarize the article's main findings; and 4) Conclusion:
Indicate the main conclusions or interpretations. The abstract should be
an objective representation of the article, it must not contain results
which are not presented and substantiated in the main text and should
not exaggerate the main conclusions.}

@@

These findings are in line with our previous report
\citep{wang_milk_2015}. Moreover, we further updated with more
comprehensive and more straightforward evidence about whether and how
certain the evidence had shown about daily consumption of milk is
contributing to a postponed stroke (mostly cerebral infarction)
mortality event among Japanese male daily milk drinker. A recent
dose-response meta-analysis of 18 prospective cohort studies had also
shown a similar negative association \citep{DeGoede2016} between milk
consumption and risk of stroke. The same meta-analysis however also
found a slightly higher risk of stroke per 200 g/day whole milk intake
from five cohort studies that were conducted on European or American
population \citep{goldbohm2011dairy, Iso1999}.

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments{All sources of funding of the study should be
disclosed. Please clearly indicate grants that you have received in
support of your research work. Clearly state if you received funds for
covering the costs to publish in open access.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{``X.X. and Y.Y. conceive and designed the
experiments; X.X. performed the experiments; X.X. and Y.Y. analyzed the
data; W.W. contributed reagents/materials/analysis tools; Y.Y. wrote the
paper.'\,'}

>>>>

%=================================================================
\documentclass[nutrients,article,To be
submitted,moreauthors,pdftex]{mdpi}

@@

% Abstract (Do not insert blank lines, i.e. \\)
\abstract{To further examine the relationship between milk intake and
stroke mortality among the Japanese population. We used}

@@

These findings are in line with our previous report
\citep{wang_milk_2015} as well as other studies conducted in East Asian
populations
\citep{umesawa2008dietary, kondo2013consumption, ozawa2017dietary, sauvaget2003intake, Talaei_2016}.
Moreover, we have further updated with more comprehensive and
straightforward evidence about whether and how certain the data had
shown about daily consumption of milk is contributing to a postponed
stroke (mostly cerebral infarction) mortality event among Japanese men.
A recent dose-response meta-analysis of 18 prospective cohort studies
had also shown a similar negative association \citep{DeGoede2016}
between milk consumption and risk of stroke. The same meta-analysis also
reported a greater reduction of risk of stroke (18\%) for East Asian
population in contrast with the 7\% less risk in the pooled overall
finding for all populations combined. Benefits of increased milk intake
might be particularly noticeable in East Asian countries where strokes
are relatively more common, and milk consumption is much lower than
those studies conducted among European or American populations
\citep{dehghan2018association}.

Possible reasons for a protective effect of milk consumption against
stroke could be interpreted as such an association may be mediated by
its content in calcium, magnesium, potassium, and other bioactive
compounds, as recommended by \citet{Iacoviello2018}. Apart from the
inorganic minerals in milk that would be helpful with health effects,
recent studies on animal models also indicated key evidence that
stroke-associated morbidity was delayed in stroke-prone rats who were
fed with milk-protein enriched diets \citep{Chiba2012, singh2016diets}.
More precisely, \citet{Singh2020} found that whey protein and its
components lactalbumin and lactoferrin improved energy balance and
glycemic control against the onset of neurological deficits associated
with stroke. Bioactive peptides from milk proteins were also responsible
for limitation of thrombosis \citep{tokajuk2019whey} through their
angiotensin convertase enzyme inhibitory potential, which might partly
explain why the effect was found mainly for mortality from cerebral
infarction in the current study.

Some limitations here are worth mentioning. First, although our object
was not to answer which type of milk is protective, but if such
information were somehow available in the JACC study database, more
detailed comparison or stratification would have been possible. Second,
despite reasonable validity of FFQ in the JACC study cohort was assessed
and confirmed, measurement errors are inevitable. Therefore, we did not
try to compute the amount of consumption by multiplying an average
volume per occasion with the frequency of intake since the random error
might be exaggerated and the observed associations may have attenuated.
Strengths of our analyses included that we have transformed the research
questions to more transparent ones that is easier for interpretation.
Direct probabilities that daily milk intake is associated with lower
hazard or delayed stroke mortality event were provided here after
thorough computer simulation.

In conclusion, the JACC study database has provided evidence that
Japanese men who consumed milk daily had lower hazard of dying from
stroke especially cerebral infarction compared with their counterparts
who never consumed milk. Time before an event of stroke mortality
occurred were slowed down and delayed among those who drank milk
regularly.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments{The authors would like to express their sincere
appreciate to Kunio Aoki and Yoshiyuki Ohno, Professors Emeritus at
Nagoya University School of Medicine and former chairpersons of the JACC
Study. The whole member of JACC Study Group can be found at
\url{https://publichealth.med.hokudai.ac.jp/jacc/index.html}. The JACC
Study has been supported by Grants-in-Aid for Scientific Research from
the Ministry of Education, Culture, Sports, Science and Technology of
Japan (MEXT, Monbu Kagaku-sho), Tokyo (grant numbers 61010076, 62010074,
63010074, 1010068, 2151065, 3151064, 4151063, 5151069, 6279102,
11181101, 17015022, 18014011, 20014026, 20390156, 26293138, and
16H06277), and Grants-in-Aid from the Ministry of Health, Labour and
Welfare, Health and Labour Sciences Research Grants, Japan
{[}H20-Junkankitou (Seishuu)-Ippan-013, H23-Junkankitou (Seishuu)-
Ippan-005, H26-Junkankitou (Seisaku)-Ippan-001, and H29-Junkankitou
(Seishuu)-Ippan-003{]}.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{``C.W. and H.Y. conceive and designed the study;
C.W. analyzed the data; C.W. wrote the first draft of the paper. A.T.
provided the database. All of the authors approved and finalized the
manuscript for publication.'\,'}
